The MacLeish Package: R Package for analyzing weather and spatial data

### 2022-06-06 joss_paper/paper.Rmd
remove unnecessary packages

```{r, echo=FALSE, results = FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(forcats)
library(leaflet)
library(dplyr)
library(imager)
library(knitr)
library(qpdf)
```

@@

```{r}
map <- leaflet() %>%
  addTiles() %>%
  addPolygons(
    data = macleish_layers[["boundary"]], 
    weight = 1, fillOpacity = 0.1
  ) %>%
  addPolygons(
    data = macleish_layers[["buildings"]], 
    weight = 1, popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["trails"]], 
    weight = 1, color = "brown",
    popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["streams"]], 
    weight = 2
  ) %>%
  addMarkers(
    data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
    popup = ~Label
  )
```

```{r leafletmap, fig.cap="Interactive `leaflet` map of the MacLeish Field Station.", out.width="50%"}
include_graphics(path = "leaflet.png")
```

@@

```{r, eval = FALSE}
tree_diameter1
```
```{r tree-diameter-1}
tree_diameter1 %>% 
  head() %>% 
  select(-module) %>% 
  kable(
    format = "latex",
    caption = "Tree diameter dataset 1.",
    booktabs = TRUE,
    escape = FALSE,
    linesep = ""
  ) %>% 
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  )
```

```{r, eval = FALSE}
tree_diameter2
```
```{r tree-diameter-2}
tree_diameter2 %>% 
  head() %>% 
  select(-module) %>% 
  kable(
    format = "latex",
    caption = "Tree diameter dataset 2.",
    booktabs = TRUE,
    escape = FALSE,
    linesep = ""
  ) %>% 
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  )
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species and position between 2010-2015."}
tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                                "emergent", "canopy", "subcanopy", 
                                "sapling")) %>%
  ggplot( aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60)) +
  facet_wrap(~year) +
  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
       title = "Distribution of Diameter Between 2010-2015") +
  theme(legend.position="bottom")
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter of Eastern Hemlock tree depending on position between 2010-2015."}
tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                                "emergent", "canopy", "subcanopy", 
                                "sapling")) %>%
  ggplot(aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_y_discrete(limits=c("Eastern Hemlock")) +
  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
       title = "Distribution of Diameter for Eastern Hemlock") +
  theme(legend.position="bottom")
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species between 2009-2016."}
tree_diameter2 %>%
  ggplot( aes(x=diameter, y=species)) +
  geom_boxplot() +
  geom_jitter(color="black", size=0.4, alpha=0.9) +
  scale_fill_viridis(discrete = TRUE, alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60)) +
  facet_wrap(~year) +
  labs(x = "Diameter (cm)", y = "Species", 
       title = "Distribution of Diameter Between 2009-2016") +
  theme(legend.position="bottom")
```

@@

```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
include_graphics("phenocam.jpeg")
```

>>>>

@@

```{r}
library(leaflet)
map <- leaflet() %>%
  addTiles() %>%
  addPolygons(
    data = macleish_layers[["boundary"]], 
    weight = 1, fillOpacity = 0.1
  ) %>%
  addPolygons(
    data = macleish_layers[["buildings"]], 
    weight = 1, popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["trails"]], 
    weight = 1, color = "brown",
    popup = ~ name
  ) %>%
  addPolylines(
    data = macleish_layers[["streams"]], 
    weight = 2
  ) %>%
  addMarkers(
    data = filter(macleish_layers[["landmarks"]], grepl("Met", Label)), 
    popup = ~Label
  )
```

```{r leafletmap, fig.cap="Interactive `leaflet` map of the MacLeish Field Station.", out.width="50%"}
knitr::include_graphics(path = "leaflet.png")
```

@@

```{r, eval = FALSE}
tree_diameter1
```
```{r tree-diameter-1}
tree_diameter1 %>% 
  head() %>% 
  select(-module) %>% 
  knitr::kable(
    format = "latex",
    caption = "Tree diameter dataset 1.",
    booktabs = TRUE,
    escape = FALSE,
    linesep = ""
  ) %>% 
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  )
```

```{r, eval = FALSE}
tree_diameter2
```
```{r tree-diameter-2}
tree_diameter2 %>% 
  head() %>% 
  select(-module) %>% 
  knitr::kable(
    format = "latex",
    caption = "Tree diameter dataset 2.",
    booktabs = TRUE,
    escape = FALSE,
    linesep = ""
  ) %>% 
  kableExtra::kable_styling(
    latex_options = c("hold_position")
  )
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species and position between 2010-2015."}
library(ggplot2)
tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                                "emergent", "canopy", "subcanopy", 
                                "sapling")) %>%
  ggplot( aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis_d(alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60)) +
  facet_wrap(~year) +
  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
       title = "Distribution of Diameter Between 2010-2015") +
  theme(legend.position="bottom")
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter of Eastern Hemlock tree depending on position between 2010-2015."}
tree_diameter1 %>%
  mutate(position = fct_relevel(position,
                                "emergent", "canopy", "subcanopy", 
                                "sapling")) %>%
  ggplot(aes(x=diameter, y=species, fill=position)) +
  geom_boxplot() +
  scale_fill_viridis_d(alpha=0.6, option="A") +
  scale_y_discrete(limits=c("Eastern Hemlock")) +
  labs(x = "Diameter (cm)", y = "Species", fill = "Position", 
       title = "Distribution of Diameter for Eastern Hemlock") +
  theme(legend.position="bottom")
```

@@

```{r, warning=FALSE, echo=FALSE, fig.cap="Boxplot of tree diameter depending on species between 2009-2016."}
tree_diameter2 %>%
  ggplot( aes(x=diameter, y=species)) +
  geom_boxplot() +
  geom_jitter(color="black", size=0.4, alpha=0.9) +
  scale_fill_viridis_d(alpha=0.6, option="A") +
  scale_x_continuous(limits=c(0,60)) +
  facet_wrap(~year) +
  labs(x = "Diameter (cm)", y = "Species", 
       title = "Distribution of Diameter Between 2009-2016") +
  theme(legend.position="bottom")
```

@@

```{r phenocam, echo=FALSE, fig.cap="Image of the MacLeish Field Station taken above retrieved from the PhenoCam Network."}
knitr::include_graphics("phenocam.jpeg")
```
